Verifying Demonstrations

### 2019-09-20 paper/DB-anon-cred.tex
Changes to \PK{\alpha, \sk: ... \land ...}

    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho} g^{\hat\rho}\)
    & \(\ProtoSendRight{R}\)
    & \(\hat A\gets A \pk_P\)
    \\

@@

    % null
    &
    & Accept if \(R =  \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and \(\Delta t 
      < t_{\max}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol actually proves \(\PK[\alpha, \sk_P][\hat A = g^\alpha 
      \hat g^{\sk_P}]\).
    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
    \ac{DBTF}.
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
\(\PK[\alpha, \sk_P][\hat A = g^\alpha \hat g^{\sk_P}]\).
\daniel{Or is it better to do \(\PK[\alpha, \sk_P][A = g^\alpha \land \hat A = 
    \hat g^{\sk_P}]\)?}
They use the agreed upon key~\(k\) as the key for \(\UWBPR\).

The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets g^\rho 
  \hat g^{\hat\rho}\).
The verifier computes \(\hat A\gets A \pk_P\), where \(A\) is the value for 
which the prover must prove knowledge of the discrete logarithm.

@@

The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
limit~\(t_{\max}\).

>>>>

    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
    & \(\ProtoSendRight{R, \hat R}\)
    & \(\hat A\gets \pk_P\)
    \\

@@

    % null
    &
    & Accept if \(R = A^{c_i} g^{s_i}\), \(\hat R =  \hat A^{c_i} \hat g^{\hat 
        s_i}\) and \(\Delta t < t_{\max}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
      \hat A = \hat g^{\sk_P}]\).
    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
    \ac{DBTF}.
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
They use the agreed upon key~\(k\) as the key for \(\UWBPR\).

The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
The verifier computes \(\hat A\gets \pk_P\).

@@

The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
not exceed the limit~\(t_{\max}\).
